---
title: "DATA 607 Week Two Assignment"
author: "Tyler Baker"
date: "9/5/2021"
output:
  html_document:
    df_print: paged
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
```

## Assignment #2

This week our task is to create a table in a SQL database and import it into R. Then we can experiment with the data.Ways to handle NULL data.

### The Setup
I started with six movies that came out over the past few years. I then asked five friends to review them on a scale of 1 to 5. If they had not seen the movie then they were told to leave it blank, which would be stored as a NULL.



```{r friends_movie_reviews}
friends_movie_reviews <- read.csv('https://raw.githubusercontent.com/tylerbaker01/SQL-Movie-Review-Table/main/friendsmoviereviews.csv')
```
# Structuring the Data
``` {r structureing the data}
str(friends_movie_reviews)
#shows the structure of the data table.
names(friends_movie_reviews) <- tolower(names(friends_movie_reviews))
#changes the column names to lower case.
friends_movie_reviews[friends_movie_reviews =="NULL"] <- NA
#R cannot read NULL, must convert NULL into NA.

friends_movie_reviews$parasite <- as.numeric(friends_movie_reviews$parasite)
friends_movie_reviews$avengers..endgame <- as.numeric(friends_movie_reviews$avengers..endgame)
friends_movie_reviews$us <- as.numeric(friends_movie_reviews$us)
friends_movie_reviews$soul <- as.numeric(friends_movie_reviews$soul)
friends_movie_reviews$sound.of.metal <- as.numeric(friends_movie_reviews$sound.of.metal)
friends_movie_reviews$knives.out <- as.numeric(friends_movie_reviews$knives.out)
#Converted each movie column into a numeric value instead of a character value.
```

## Data Experimentation

What is the best way to handle NA's. I thought Cassie's view was quite clever therefore, I will do as she did to see what happens to the data. First I will allow the NA's to be counted as a 1. Then I will allow my NA's to be counted as a 3. I will also convert NA's into 2 to account for people that don't want to watch a movie because they just didn't seem interested in it, they don't absolutely hate it, they just were disinterested when they saw the previews. The only downfall with this trick is that it doesn't account for instances where someone thinks they will not like a movie, but ends up watching and loves it. There are simply movies that surprise us.

```{r data experimentation}
friends_movie_reviews_one <- friends_movie_reviews %>% mutate_all(~replace(., is.na(.), 1))
#Turned NA's into the value 1.
friends_movie_reviews_two <- friends_movie_reviews %>% mutate_all(~replace(., is.na(.), 2))
#Turned NA's into 2.
friends_movie_reviews_three <- friends_movie_reviews %>% mutate_all(~replace(., is.na(.), 3))
#Turned NA's into 3.
str(friends_movie_reviews_one)
```

#Finding Averages

```{r finding averages}
#Column Wise


colMeans(friends_movie_reviews_one[sapply(friends_movie_reviews_one, is.numeric)])
movie_averages_one<- c("avg_rating", 2.9, 3.53, 3.97, 2.83, 2.933, 2.689, 3.14)

#movie_averages <- colMeans(friends_movie_reviews_one[sapply(friends_movie_reviews_one, is.numeric)])
##The average of each column is appearing in the previous column. not sure how to fix.
friends_movie_reviews_one <- rbind(friends_movie_reviews_one, movie_averages_one)
#add a row for the averages

colMeans(friends_movie_reviews_two[sapply(friends_movie_reviews_two, is.numeric)])
movie_averages_two <- c("avg_rating", 3.2, 3.6, 4.4, 3.0, 3.2, 2.8, 3.367)
friends_movie_reviews_two <- rbind(friends_movie_reviews_two, movie_averages_two)
#Mean value of the columns turned into a row through manual input.
##Ask professor about how to turn this process into a function.
colMeans(friends_movie_reviews_three[sapply(friends_movie_reviews_three, is.numeric)])
movie_averages_three <- c("avg-rating", 3.6, 3.8, 4.6, 3.2, 3.4, 3.0, 3.6)
friends_movie_reviews_three <- rbind(friends_movie_reviews_three, movie_averages_three)

#Convert Columns to Numeric... again
#friends_movie_reviews_one
friends_movie_reviews_one$parasite <- as.numeric(friends_movie_reviews_one$parasite)
friends_movie_reviews_one$avengers..endgame <- as.numeric(friends_movie_reviews_one$avengers..endgame)
friends_movie_reviews_one$us <- as.numeric(friends_movie_reviews_one$us)
friends_movie_reviews_one$soul <- as.numeric(friends_movie_reviews_one$soul)
friends_movie_reviews_one$sound.of.metal <- as.numeric(friends_movie_reviews_one$sound.of.metal)
friends_movie_reviews_one$knives.out <- as.numeric(friends_movie_reviews_one$knives.out)

#friends_movie_reviews_two
friends_movie_reviews_two$parasite <- as.numeric(friends_movie_reviews_two$parasite)
friends_movie_reviews_two$avengers..endgame <- as.numeric(friends_movie_reviews_two$avengers..endgame)
friends_movie_reviews_two$us <- as.numeric(friends_movie_reviews_two$us)
friends_movie_reviews_two$soul <- as.numeric(friends_movie_reviews_two$soul)
friends_movie_reviews_two$sound.of.metal <- as.numeric(friends_movie_reviews_two$sound.of.metal)
friends_movie_reviews_two$knives.out <- as.numeric(friends_movie_reviews_two$knives.out)

#friends_movie_reviews_three
friends_movie_reviews_three$parasite <- as.numeric(friends_movie_reviews_three$parasite)
friends_movie_reviews_three$avengers..endgame <- as.numeric(friends_movie_reviews_three$avengers..endgame)
friends_movie_reviews_three$us <- as.numeric(friends_movie_reviews_three$us)
friends_movie_reviews_three$soul <- as.numeric(friends_movie_reviews_three$soul)
friends_movie_reviews_three$sound.of.metal <- as.numeric(friends_movie_reviews_three$sound.of.metal)
friends_movie_reviews_three$knives.out <- as.numeric(friends_movie_reviews_three$knives.out)

#Row Wise
friends_movie_reviews_one$Avg_review = rowMeans(friends_movie_reviews_one[2:7])
#Calculated each friend's rating average, where NULL's =1.
friends_movie_reviews_two$Avg_review = rowMeans(friends_movie_reviews_two[2:7])
#Calculated each friend's rating average, where NULL's =2.
friends_movie_reviews_three$Avg_review = rowMeans(friends_movie_reviews_three[2:7])
#Calculated each friend's rating average, where NULL's =3.


```

#Graph
We are just now going over graphing in 606. 

```{r graph}

```

#Conclusion
For the conclusion I want to compare how "Parasite" and "Us" perform in each orientation of NA. I chose these two because "Parasite" had the most NA's and I chose "Us" because it had perfect scores expect for the one NA.

##Parasite
The true average of "Parastie" is 4. We are searching to see which orientation is the closest to the true average. If NA=1 we get an average of 2.9. If NA=2 we get an average rating of 3.2. Finally, if we set NA=3 we get 3.6. Thus, in the case of Parasite it was best to set NA=1.

##Us
The true average of "Us" is 5. Again, we want to find which orientation gets the closest to 5. If NA=1 we get an average of 3.97, If we set NA=2 we get an average of 4.4. Finally, if we set NA=3 we get an average of 4.6. In this case, setting NA=3 was best decision. 

##Final thoughts
Since the two cases do not agree, I do not think that substituting any of these values is the best option. I would guess that substituting the NA's with the true average would probably be the way to produce the most accurate values.
